%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Android Software Engineer} % Job title
  {Carv} % Organization
  {London, UK} % Location
  {Aug, 2021—Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked closely with product and data science teams to bring new features into the app.}
      \item {Developed cross-platform functionalities through a shared Rust codebase.}
      \item {Strengthen the code base with the introduction of clean architecture principles.}
      \item {Helped CS to solve android specific issues.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Android Software Engineer} % Job title
  {Planet Idea Srl.} % Organization
  {Turin, Italy} % Location
  {May 2020—Aug. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and developed a modular android SDK providing our most common use cases for product prototyping.}
      \item {Been part of a team of four that defined all the aspect of the android app development such as architecture design, code conventions and standards, CI/CD pipelines.}
      \item {Refactored legacy application to enforce code and architectural standards.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Android Software Engineer \& Tech Lead} % Job title
  {The Lab.} % Organization
  {Turin, Italy} % Location
  {Mar. 2017—May 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {In the last year, I was responsible for a team of five.}
      \item {Developed brand new Android application.}
      \item {Built a tax calculation REST service consumed by a web-based application for an accountant agency.}
      \item {Promoting standards such CI/CD, test automation and code review.}
      \item {Mentoring junior developer.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Fullstack Developer} % Job title
  {Assioma.Net} % Organization
  {Turin, Italy} % Location
  {Nov. 2015—Mar. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Maintained and developed a legacy warehouse management application.}
      \item {Development of internal toolings and SDKs.}
    \end{cvitems}
  }
\end{cventries}
